Dark Control:\\ Towards a Unified Account of Default Mode Function\\ by Markov Decision Processes

### 2017-11-28 paper/paper.tex
Add embryo of two new experiments in Box 2

>>>>

\item Experiment (Humans): We hypotherize that time horizon should be modulated by different factors such as age, stress, and impulsivity. Using a temporal discounting task, we can measure how the time horizon could be affected at the behavioral level, and then trace back its potential representation at the neural level. Experimental design can be between groups (by age or with a impulsive population like chronic gamblers or drug addicts), or within group using a stress.

% To exam-ine this question, Fellows and Farah (2005) investigated the effects of dorsolateral frontal (DLF) and ventromedial frontal (VMF) lobe damage on two aspects of temporal foresight—namely, temporal discounting and the futuretime perspective (measuredby an adaptation of Wallace’s [1956] list of future life events).

\item Experiment (Animals): how synaptic epigenesis between DMN nodes can form a neural correlate of the policy matrix update? % Simulations:
